A Bayesian model for the K2 data

### 2013-10-23 text/prob_model/prob_model.tex
prob mod 1st shot

\title{A Bayesian model for the K2 data}
\author{Michael Franke}
\date{}

@@

>>>>

\title{A Bayesian model for the K2 data}
\author{}
\date{}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{pics/Posterior_TF.pdf}
  \caption{Posterior over weights for target readings in
    target-related control conditions.}
  \label{fig:Posterior_TF}
\end{figure}

Using MCMC sampling, we obtain estimates for the posterior of the
latent parameters given the data. We are most interested in the level
of credence we should place on the weights of target readings in
critical conditions. But to check whether the model yields sensible
results we first look at the preference-related control
conditions.

Estimates for the posteriors over weights for target-related controls
are plotted in Figure~\ref{fig:Posterior_TF}. The results are exactly
as we would expect them to be. Given our data, we should believe that
the late-closure reading is more prominent. But the level of
prominence varies with accentuation. Under prosody that we
hypothesized would favor the late-closure reading, the contrast is
most pronounced. Contrarily, accentuation that we hypothesized favors
the early-closure reading we are no longer justified in believing that
the late-closure reading is certainly preferred (witness the clearly
overlapping 95\% confidence regions).

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{pics/Posterior_T.pdf}
  \caption{Posteriors over weights for target readings in critical
    conditions. Colored lines below the actual plots indicate 95\%
    confidence intervals.}
  \label{fig:Posterior_T}
\end{figure}

Turning to the critical conditions, estimates of posteriors over
weights given our data are given in Figure~\ref{fig:Posterior_T}. We
only have marginal reasons to believe that global readings have any
non-negligible weight data in the AS-A condition. Apart from this, if
the model is true, the data corroborates the belief that the literal
reading is strongly preferred over the local reading over the global
reading (again witness the non-overlapping 95\% confidence
regions). We also see the expected general effect of intonational
markedness. Qualitatively speaking, the preference for literal
readings appears less pronounced in the accented conditions.

\todo[inline]{still to be added: posteriors over $q$ and errors $e_k$}

\paragraph{Model validation.} We should also check whether the model
is actually a suitable model to predict the observed data. Posterior
predictive checks indicate that it is. Figures~\ref{fig:Posterior_TF}
and \ref{fig:Posterior_T} show simulated samples of answer patterns
that the model predicts under the posterior values for the latent
parameters. Everything looks almost perfect, with the only exception
the estimation of global readings in the ES-conditions.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{pics/PPC_TF.pdf}
  \caption{Posterior predictive check for the target-related control
    conditions. The colored dots on the plots indicate the actual
    observed numbers of choices. Intuitively speaking, the ``higher''
    the dot on the curve, the more likely does the model (under the
    posterior values for its parameters) predict the data (on which
    the posterior estimate is based).}
  \label{fig:Posterior_TF}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{pics/PPC_T.pdf}
  \caption{Posterior predictive check for the target-related control
    conditions.}
  \label{fig:Posterior_T}
\end{figure}
